Using an SMT engine to generate Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-21 2017-Xudong-SMT/ActaInformatica.tex
today's end of the day commit...

        In this example we use \emph{synchronised
          actions}, to express actions that cannot be further synchronised, likesimilar to the
        $\tau$ silent action of CCS. We denote them as any action expression with the text
        underlined, as e.g. $\underline{\delta(x_2)}$. Such
        synchronised actions do not play any special role for defining
        the semantics of pNets, but as one can expect, will be crucial
        for defining weak equivalences.

@@

%%\subsection{simple communication protocol} specification and implementation;

>>>>

        In this example we use \emph{synchronised
          actions}, to express actions that cannot be further synchronised, similar to the
        $\tau$ silent action of CCS. We denote them as any action expression with the text
        underlined, as e.g. $\underline{\delta(x_2)}$. Such
        synchronised actions do not play any special role for defining
        the semantics of pNets, but as one can expect, will be crucial
        for defining weak equivalences.

@@

\begin{figure}[~tb]
\centerline{ 
  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
    {A_0 \xrightarrow{a1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x2)}_P,\,
                            \xrightarrow{acc(x2)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
    {A_1 \xrightarrow{a3} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
    {B_0 \xrightarrow{b1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y2)}_P,\,
                            \xrightarrow{acc(y2)}_Q \}, \\
                                        v=0, \\
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
    ot'_3  =& \openrule{
                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
    {B_1 \xrightarrow{b2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

The open automata generated for the 2 encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}. We have shown in \ref{Forte} how to
prove that these two automata are bismilar.

Now 
%%\subsection{simple communication protocol} specification and implementation;
